Network Structure, Efficiency, and Performance in WikiProjects

### 2017-08-05 paper.tex
More content.

The node degree distribution is the simplest structural property we analyze for WikiProject
coeditor networks.
The in-degree (out-degree) of a node is the number of edges to (from) that node.
Taking the average of either in-degree or out-degree gives the same value:
the {\em mean degree} of the network.
In our context, the mean degree represents how many others a given editor has collaborated with.
We also consider the {\em skewness} of the in-degree and out-degree distributions.
A large positive degree skewness value for a WikiProject coeditor network
implies that a small number of editors have a very large number of collaborators,
while a small positive value implies that the editors having the most collaborators
don't have too many more than a typical editor.

Path length

Min-cut

@@

OLS

@@

\section{Acknowledgements}
TODO

>>>>

The node degree distribution is the simplest structural property we analyze for WikiProject
coeditor networks.
The in-degree (out-degree) of a node is the number of edges to (from) that node.
Taking the average of either in-degree or out-degree gives the same value:
the {\em mean degree} of the network.
In our context, the mean degree represents how many others a given editor has collaborated with.
We also consider the {\em skewness} of the in-degree and out-degree distributions.
A large positive degree skewness value for a WikiProject coeditor network
implies that a small number of editors have a very large number of collaborators,
while a small positive value implies that the editors having the most collaborators
don't have many more than a typical editor.

We also calculate the characteristic path length for each WikiProject coeditor network.
The {\em distance} from editor A to editor B is the length of the shortest path from A to B.
The {\em characteristic path length} is the mean distance between all editor pairs.
If no path exists between two editors, we exclude that pair from the mean.
For brevity, we will simply refer to this quantity as the {\em path length}.
The path length represents how quickly information can move through the network.
Networks with longer paths require more interactions for information to propagate through
the network.

Our final network measure quantifies the connectivy of a project's coeditor network using
min-cut size.
The minimum $st$-cut between nodes $s$ and $t$ is the set of edges that must be removed in order that
no path exists from $s$ to $t$.
The minimum cut (min-cut) of a graph is the smallest minimum $st$-cut over all node pairs $st$. 
The size of the graph min-cut quantifies the connectivity of a graph,
but only incorporates information about edges lying on paths crossing the min-cut.
Instead, we use the mean size of all minimum $st$-cuts, which we refer to as the
{\em mean min-cut}.
This measure quantifies the number of redundant paths information can take through the network.
Networks with higher redundancy are more resilient to errors on one path \cite{}
and allow innovation to propagate through complex contagion,
in which innovations are only adopted after multiple exposures thorugh different sources
\cite{}.

@@

OLS, controls

@@

\section{Acknowledgements}
Daniel Romero.
Danielle Livneh, Karthik Ramanathan.
Yan Chen, Tanya Rosenblat.
MIT Center for Civic Media.
Cooperation Working Group at the Harvard Berkman-Klein Center.
School of Information.
